Tutorial_2

### 2024-09-22 Tutorial_2.Rmd
update Tutorial 2

```{r save-plot-effects, eval=F}
ggsave("Tutorial_2_Bayesian/figures/M4effects_con_incon_trial1000.png", width = 12, height = 12, dpi = 600)
```

@@

>>>>

```{r save-plot-effects, eval=F}
ggsave("Tutorial_2_Bayesian/figures/M4effects_con_incon_trial1000.png", width = 12, height = 12, dpi = 300)
```

@@

```{r save-plot-fit-hazard, eval=F}
ggsave("Tutorial_2_Bayesian/figures/M4effects_subject6.png", width = 10, height = 10, dpi = 300)
```
